---
title: "Reproducible and open scientific workflow toolkit"
subtitle: "An introduction to rostools"
author: "Luke W. Johnston"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducible and open scientific workflow toolkit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


In addition to the main functions, there are several `include_*()`
style functions available to add other, maybe less common, files. So far
there are:

- `include_rfigshare_script()` to send portions (or all) of your code to
[figshare](https://figshare.com/) for others to confirm or use your code and
analysis workflow.
- `include_mit_license()` to add a MIT license to your code, so that you
explicitly allow others to re-use your code without legal issues coming up.
Works well in conjunction with the above function.
- `include_strobe()` to add a STROBE checklist. This is very specific to
epidemiological research (which I do), so not all users will need this.

You can use them by opening up the new project `.Rproj` (RStudio) file and run
them in the console as:

```{r, eval=FALSE}
prodigenr::include_rfigshare_script()
prodigenr::include_mit_license()
prodigenr::include_strobe()
```



```{r}
devtools::load_all()
library(desc)
library(prodigenr)
path <- tempdir()
setup_project("newproject", path = path)
list.files(path = path)
x <- desc::description$new(file = file.path(path, "newproject", "DESCRIPTION"))
x$get("Authors")
x$set_authors()
```

